Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2020-06-19 Silvers_cfmip.tex
added Webb et al. and Eyring et al references for the CMIP6 and CFMIP documentation papers.  added a new table with experiments.  updated some of terrible captions.

\subsection{COSP}
In order to compare the observed and modeled clouds as consistently as possible across multiple platforms 
GFDL has implemented a collection of satellite simulators which are part of the 
CFMIP (Cloud Feedback Model Intercomparison Project; see Webb et al., 2017).  Satellite simulator
are software tools that are used in coordination with GCMs to allow for model variables 
to be translated to variables that are more directly comparable with what satellites observe.  
These simulators are often referred to as the CFMIP Observation Simulator Package (COSP); for
details see Bodas-Salcedo et al. 2011.  This paper highlights simulators of the algorithms for 
four satellite datasets: ISCCP (the International Satellite Cloud Climatology Project), 
MODIS (the Moderate Resolution Imaging Spectroradiometer), 
MISR (the Multiangle Imaging Spectro-Radiometer), and 
CALIPSO (the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation; 
Chepfer et al., 2010; Cesana and Chepfer, 2013).  By using multiple complimentary satellite 
datasets and simulators we can benefit from the different strengths of each satellite while largely 
minimizing the known problems and discrepancies of the observational data sets.

@@

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).  The \textit{amip p8K} is not a separate experiment but
shows the feedbacks computed from the \textit{amip-p4K} when the \textit{amip-m4K} is the control experiment.}
    \begin{tabular}{*{8}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2  & 1\% $CO_2$  \\ \hline
    Net          &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
    \\
    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11          & 0.65   & -0.30  \\  
    \\
    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10          & 0.14  & 0.02    \\  
    \\
    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21         & 0.5  & -0.32       \\  
    \\
    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03         & -1.7   & -1.94      \\  
    \\
    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30          & 0.6    & 0.76        \\  \hline

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \caption{Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
  shows the measured CRE from CERES-EBAF 
  observations compared to simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
  shown at left is the simulated CRE from three fully coupled experiments with CM4.0 (\textit{historical},
  \textit{abrupt-4xCO$_2$}, and \textit{1pctCO$_2$}).  Right panel, the CRE feedback from four 
  amip-like experiments.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
  been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Silvers_cfmip_SinglePanelFig.pdf}
  \caption{Cloud fraction for experiments with warming.  Cloud fractions are shown for the upper-, mid-, and low-level 
  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the right column
  shows values relative to the \textit{amip} experiment.  For the coupled model experiments
 \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted.  
  For reference cloud fraction from the 
 \textit{historical} (purple) and \textit{amip} are also shown.}
  \label{fig:CF_warming}
\end{figure}

@@

@@

@@

% how exactly should I cite the CERES data?  Looking here: https://eosweb.larc.nasa.gov/project/ceres/ebaf_ed4.1. I don't see a 
% particular paper to cite, just DOI's.  The info from ncdump implies that the data extends along 200003-201809, which is confirmed by
% 223 time steps that are presumably monthly....  but in the global attributes section of the output from ncdump it states: 
%:title = "CERES EBAF TOA and Surface Fluxes. Monthly Averages and 07/2005 to 06/2015 Climatology." ;
%                :institution = "NASA Langley Research Center" ;
%                :Conventions = "CF-1.4" ;
%                :comment = "Climatology from 07/2005 to 06/2015" ;
%                :version = "Edition 4.1; Release Date May 28, 2019" ;
%                :DOI = "10.5067/TERRA-AQUA/CERES/EBAF_L3B004.1"

>>>>

\subsection{COSP}
In order to compare the observed and modeled clouds as consistently as possible across multiple platforms 
GFDL has implemented a collection of satellite simulators which are part of the 
CFMIP (Cloud Feedback Model Intercomparison Project; see \cite{Webb_etal_2017}).  Satellite simulator
are software tools that are used in coordination with GCMs to allow for model variables 
to be translated to variables that are more directly comparable with what satellites observe.  
These simulators are often referred to as the CFMIP Observation Simulator Package (COSP); for
details see Bodas-Salcedo et al. 2011.  This paper highlights simulators of the algorithms for 
four satellite datasets: ISCCP (the International Satellite Cloud Climatology Project), 
MODIS (the Moderate Resolution Imaging Spectroradiometer), 
MISR (the Multiangle Imaging Spectro-Radiometer), and 
CALIPSO (the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation; 
Chepfer et al., 2010; Cesana and Chepfer, 2013).  By using multiple complimentary satellite 
datasets and simulators we can benefit from the different strengths of each satellite while largely 
minimizing the known problems and discrepancies of the observational data sets.

@@

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).  The \textit{amip p8K} is not a separate experiment but
shows the feedbacks computed from the \textit{amip-p4K} when the \textit{amip-m4K} is the control experiment.}
    \begin{tabular}{*{8}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2  & 1\% $CO_2$  \\ \hline
    Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
    \\
    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11          & 0.65   & -0.30  \\  
    \\
    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10          & 0.14  & 0.02    \\  
    \\
    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21         & 0.5  & -0.32       \\  
    \\
    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03         & -1.7   & -1.94      \\  
    \\
    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30          & 0.6    & 0.76        \\  \hline

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
  shows (in black) the measured CRE from two versions of the CERES-EBAF observations.   compared to 
  simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
  shown at left is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (1950-2014),
  \textit{abrupt-4xCO$_2$} (101-150), and \textit{1pctCO$_2$} (101-150)) and the AM4.0 amip experiment.  Right panel, the CRE feedback from four 
  of the amip-like experiments from CFMIP.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
  been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CF_figure9.pdf}
  \caption{Cloud fraction for experiments with warming.  Cloud fractions are shown for the upper-, mid-, and low-level 
  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the middle column
  shows values relative to the PI control experiment and the right column
  shows values relative to the \textit{amip} experiment.  For the coupled model experiments
 \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted while for the 
 \textit{historical} experiment the years 1950-2014 are used.  
  For reference cloud fraction from the 
 \textit{historical} (purple) and \textit{amip} are also shown.}
  \label{fig:CF_warming}
\end{figure}

@@

\appendix
\section{Experiments and Data}

Tables A1 and A2 describe the details of the observational data sets used and the various model experiments that 
have been used in this study.  All model experiments were conducted with the GFDL AM4.0 atmospheric general 
circulation model (Z18a,b), or in the case of the coupled experiments, the GFDL CM4.0 coupled general circulation 
model \cite{Held_etal_2019}. 
All experiments are taken from GFDL's contribution to CMIP6, either the DECK experiments, or experiments from CFMIP.
For additional general details about the experiments see \cite{Eyring_etal_2016} and \cite{Webb_etal_2017}.  All of the 
data used to analyze these experiments is hosted by the Earth System Grid Federation (ESGF) and is available at 
https://esgdata.gfdl.noaa.gov/search/cmip6-gfdl.

 \begin{table}
\begin{center}
\caption{Experiments used.   Should I list the years the experiment simulate or just the years used in the analysis?}
    \begin{tabular}{*{4}{c}}
    \hline
    \hline
 Experiment & Class & Configuration & Years   \\ \hline
    historical        &   DECK      &  atmosphere \& ocean   &  Jan 1950 -Dec 2014               \\ 
    \\
    abrupt 4xCO2   & DECK       &  atmosphere \& ocean       & 150 years  \\  
    \\
    1pct CO2   & DECK        &  atmosphere \& ocean  & 150 years \\  
    \\
    PI Control  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
    \\
    amip  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
    \\
    amip +4K  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
    amip -4K   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
    amip Future 4K  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
    aqua control        & CFMIP  & atmosphere  & 10 years \\
    aqua +4K.  & CFMIP    & atmosphere  &  10 years \\ \hline

@@

% \begin{sidewaystable}
% \caption{ Observational Data Sets Used in This Paper}
% \centering
% \begin{tabular}{l l}
% \hline
% Data  & Description  \\
% \hline
%   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed2.8   \\
%                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 2.8  \\
%                                     & Reference: Loeb et al. (2009); Smith et al. (2011).  \\
%                                     & URL: \url{http://ceres.larc.nasa.gov/documents/DQ_summaries/CERES_EBAF_Ed2.8_DQS.pdf}.   \\
%   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed4.1   \\
%                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 4.1  \\
%                                     & Reference:   \\
%                                     & URL: \url{http://ceres.larc.nasa.gov}.   \\
%   Cloud amount and optical depth (dates) & Short name:  MISR   \\
%                                                                   &  Long name: Multi-angle Imaging SpectroRadiometer.  \\
%   Cloud amount and optical depth (dates)  & Short name: MODIS  \\
%                                                                   & Long name: Moderate Resolution Imaging Spectroradiometer.  \\
%   Cloud amount and optical depth (dates)  & Short name: ISCCP   \\
%                                                                   & Long name: International Satellite Cloud Climatology Project   \\
%                                                                   & Reference: Rossow and Schiffer (1991); Pincus et al. (2012)   \\
%                                                                   & URL: \url{ftp://ftp.climserv.ipsl.polytechnique.fr/cfmip/ISCCP}     \\
%   Cloud amount  & Short name: CALIPSO   \\
%                           & Long name: Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations   \\
%                           & Reference: Chepfer et al. (2010); Cesana and Chepfer (2013)      \\
%    \hline
% \multicolumn{2}{l}{$^{a}$Footnote text here.}
% \end{tabular}
% \end{sidewaystable}

@@

% how exactly should I cite the CERES data?  Looking here: https://eosweb.larc.nasa.gov/project/ceres/ebaf_ed4.1. I don't see a 
% particular paper to cite, just DOI's.  The info from ncdump implies that the data extends along 200003-201809, which is confirmed by
% 223 time steps that are presumably monthly....  but in the global attributes section of the output from ncdump it states: 
%:title = "CERES EBAF TOA and Surface Fluxes. Monthly Averages and 07/2005 to 06/2015 Climatology." ;
%                :institution = "NASA Langley Research Center" 
%                :Conventions = "CF-1.4" ;
%                :comment = "Climatology from 07/2005 to 06/2015" ;
%                :version = "Edition 4.1; Release Date May 28, 2019" ;
%                :DOI = "10.5067/TERRA-AQUA/CERES/EBAF_L3B004.1"
